Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-07-23 content.tex
Point to supplementary materials

All the figures shown in this section are shown as-is, without any
aesthetical modifications..

>>>>

All the figures shown in this section are shown as-is, without any
aesthetical modifications. Figures showing the full workflow 
and tables showing the effective sample sized (a measure
of inference quality) can be found in the supplementary materials.
